%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Populi, Ltd.} % Organization
    {Rome, Italy} % Location
    {Jan. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed and tested a Rails event scheduling and booking system with an integrated marketplace, a marketplace api to be integrated in mobile apps, integration with several external systems (Viator, Get Your Guide, Globol, Rezdy)}
        \item {Developed an API integrator in Elixir and Phoenix for major tourism portals (Viator, Get Your Guide, Rezdy, TourCMS, Bokun etc.)}
        \item {Designed and developed an electronic invoicing system for a large internal app managing thousands of monthly invoices, credit notes, refunds}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager \& Software Engineer} % Job title
    {ASTRAL S.p.A.} % Organization
    {Rome, Italy} % Location
    {Dec. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used Engineering Study as Business Requirents and designed and developed an internal software to show surveyed road deteriorations.}
        \item {Developed a surveying alphabet to ease surveyor's job.}
        \item {Added deterioration feature to existing road survey company software.}
        \item {Added ShapeFile exports subdivided by lane of all the road deteriorations.}
        \item {Services deployed through Docker.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Microservices Developer} % Job title
    {NearIT} % Organization
    {Bergamo, Italy} % Location
    {Nov. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing features for backend microservices using ruby to call AWS Lambda functions written in python. Developing features for go microservices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Docker Base Course Trainer} % Job title
    {Ericcson S.p.A.} % Organization
    {Genoa, Italy} % Location
    {03-06 Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained two groups of developers on Docker.}
        \item {Same contents of official Docker course.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mastering Docker - Technical Reviewer} % Job title
    {PACKT} % Organization
    {Rome, Italy} % Location
    {Nov. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical Review of Docker book.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager \& DevOps \& Senior Developer} % Job title
    {Makeplan S.a.s.} % Organization
    {Rome, Italy} % Location
    {Jul. 2015 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architecture a major refactoring of a monolithic Rails app into microservices that can easily be deployed in the cloud.}
        \item {Develop the ruby client to connect and communicate with OrientDB.}
        \item {Develop a multitenant ruby API infrastructure through Json Web Token authentication and authorization.}
        \item {Choose technology and design a web based CAD application designed to be a replacement fo AutoCAD allowing imports from DWGs and using the same keyboard shortcuts for a seamless transition experience.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer for activity DICEA14PR098} % Job title
    {Dipartimento di Ingegneria civile, edile e ambientale - Università di Roma "La Sapienza"} % Organization
    {Rome, Italy} % Location
    {Dec. 2014 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Won a call for tender with University of Rome "La Sapienza".}
        \item {Offer the needed IT support to develop a real time dynamic photogrammetric technology platform for qualification, management and monitoring of airfields' pavimentations and for reducing the risk of FOD (Foreign Object Damage) presence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager, System Administrator and Developer} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Aug. 2014 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Plan, implement and deploy a company file sharing application like dropbox.}
        \item {The application allow for file sharing across geographically distributed sites through the use of owncloud version 7.}
        \item {Data is safely distributed and replicated through a set of glusterfs distributed and replicated volumes.}
        \item {Requests to owncloud are proxied through HAProxy and terminate in a nginx ssl enabled server.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager, System Administrator and Developer} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jan. 2014 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research project to plan, implement and deploy a private cloud.}
        \item {Implemented a docker based private cloud with service discovery for high availability and scaling.}
        \item {Internal Rails 4 application modified and deployed on the private cloud backed by a PostgreSQL cluster.}
        \item {Requests to owncloud are proxied through HAProxy and terminate in a nginx ssl enabled server.}
        \item {Designed and developed an internal tool for reporting crash test activities.}
          \begin{cvsubentries}
            \cvsubentry{}{SVG drawing of crash test dynamics}{}{}
            \cvsubentry{}{PDF generation with digital signature of all needed parties}{}{}
          \end{cvsubentries}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager and Developer} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jan. 2013 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research project to create and visualize an algorithm for Road Protection Scores and Star Ratings suitable for italian roads.}
        \item {Identified road indicators that can affect road safety.}
        \item {Tested indicators model with some italian roads.}
        \item {Designed, developed and deployed a rails/google maps app to calculate RAPP scores and Star Ratings for italian roads.}
        \item {Integrated into GeoMap app developed for the same organization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager and Developer} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jun. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a real time dashboard in Visual Basic .NET for road surveying vehicle.}
        \item {The dashboard collects data from a GigE camera, a road profile grabber with two lasers and two accelerometers and an IMU unit.}
        \item {Data Acquisition is made through National Instruments NIDaq.}
        \item {The dashboard simplifies the acquisition and recording of data using different kind of graphs to show data series.}
        \item {The dashboard was in production on two high efficiency vehicles.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Administrator} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jan. 2012 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned, implemented and deployed virtualized MAIS (Massive Array of Inexpensive Servers) to support business processes.}
        \item {The server's array is composed of HP Microservers with vSphere 5 virtualization.}
        \item {Managed services: Firewalling/VPN, Fileserver with TimeMachine like features, Git server, Mail Server, DNS, HAProxy, GlusterFS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Manager and Developer} % Job title
    {Progetti e Servizi S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jan. 2011 - Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed and deployed a full stack rails 3 app with google earth plugin integration called GeoMap.}
        \item {App automatically generates kml files for app models which are read into google earth and displayed accordingly.}
        \item {App has an administrative dashboard which aggregates and displays data through d3.js and an administrative backend.}
        \item {The application is deployed into two companies and is used to plan street maintaining.}
        \item {Designed, developed and deployed a ruby script to generate acoustic KMZ maps with coordinates conversion.}
        \item {Gis data manipulation and translation (DXF, SHP, KML, XLS).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Founder and member of the board} % Job title
    {MSEmploy} % Organization
    {Paris, Fance} % Location
    {Jun. 2007 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planning and following website development team to build a job board for Microsoft Professionals (actually www.msemploy.com).}
        \item {Got specifications from pre existing ASP web app and its developer.}
        \item {Checked website specifications with development team and stakeholders.}
        \item {Followed development team on behalf of the stakeholders.}
        \item {Tested website.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Chief Technology Officer} % Job title
    {PCSNET S.r.l.} % Organization
    {Rome, Italy} % Location
    {Jan. 2003 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Network Management: built local domain, forum and sharepoint collaboration site with Microsoft Small Business 2003.}
        \item {Implemented new functionalities on existing C\# Web Site and Managed content update.}
        \item {Managed International Partner Development: part of Microsoft Learning Advisory Board for 18 months with objective to report and advice on learning needs and market.}
        \item {Migrated existing website to new Joomla framework and planned, implemented and deployed SEO optimization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Microsoft Certified Trainer} % Job title
    {PCSNET S.r.l.} % Organization
    {Rome, Italy} % Location
    {Feb. 2001 - Dec. 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Classroom training on Microsoft and Linux technologies.}
        \item {MOC 2274 - Managing a Microsoft Windows Server 2003 Environment.}
        \item {MOC 2275 - Maintaining a Microsoft Windows Server 2003 Environment.}
        \item {MOC 2276 - Implementing a Microsoft Windows Server 2003 Network Infrastructure: Network Hosts.}
        \item {MOC 2277 - Implementing, Managing, and Maintaining a Microsoft Windows Server 2003 Network Infrastructure: Network Services.}
        \item {MOC 2823 - Implementing and Administering Security in a Microsoft Windows Server 2003 Network.}
        \item {LPI Linux Essentials.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
